---
title: "Practice"
author: "Stacy"
date: "1/13/2020"
output:
  html_document: default
  word_document: default
editor_options: 
  chunk_output_type: console
---
.
```{r}
library(tidyverse)
mobile<-read_csv("https://raw.githubusercontent.com/vmandela99/Class-assignment-12th-july-2019/master/mobilemoney_data.csv")
```

## report on summary

skimr::skim(mobile)

The data has 28 columns and 2509 rows. There exists 23 character column frequency and 5 numeric column type frequency. There are no group variables.There are three districts in total. There are 7 types of accounts, 2 gender types and urban types


#how many account types are there
```{r}
mobile %>% count(account_type, sort = T)

```
The highest number of people have mobile number tranfer with 825 people having it.The least number of people have online bank account:12. The number of people with VSLA Account is 669.The number of people with a Bank Account are 323.131 people have no account type. MFI account has 82 people


#which districts have many people
```{r}
mobile%>%count(district, sort=TRUE)

```
The district with the most number of accounts is District_C with 856 accounts whereas the district with the least number of accounts is District_A with 815 accounts. District_B has 838 accounts


#what percentage of people from district A have Sacco accounts (from the  entire data)
```{r}
mobile%>% count(district, account_type) %>% mutate(percent=n/sum(n)*100)

```
In the entire data 5.9% of the people are from district A and have a Saccp account


#what percentage of people from district A have Sacco accounts (filtering from district A)
```{r}
mobile%>% filter(district == "District_A") %>%count(district, account_type) %>% mutate(percent=n/sum(n)*100)

```
18.92 of the people from district A have a Sacco account

#how many grades completed are there
```{r}
mobile%>%count(highest_grade_completed, sort=T)

```
Primary 6 has the highest number of grades completed of 671. other has the lowest number of grades completed of 12.

#what is the largest weight in the survey

```{r}
max(mobile$weight)
```
The largest weight is 4812.165

#what percentage of people in the university have mobile money accounts
```{r}
mobile%>%filter(highest_grade_completed == "university")%>% count(account_type)%>%mutate(percent=n/sum(n)*100)


```
32.4% of the university students have a mobile account.

#how many account types are there
##graph
```{r}
mobile %>% count(account_type) %>% ggplot(aes(x=account_type,y=n)) + geom_col()

```
The mobile money has the tallest bar whereas the online bank  bar is the shortest 
#which districts have many people
```{r}
mobile%>%count(district)%>%ggplot (aes(x=district, y=n))+ geom_col()

```
The three bars are of equal length